---
title: "Untitled"
output: html_document
date: "2022-11-10"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1)  

<!-- -->

            # here, we won't account for SD as we are only computing what we "expect" to have at the end of the time frame. So simply multiplying our investment by the avg, and adding the yearly investment will give us the right answer
            stock = seq(0, 100, 5)
            avg = c(5.09,5.4,5.7,6,6.29,6.57,6.84,7.11,7.37,7.62,7.87,8.11,8.34,8.56,8.78,8.99,9.19,9.38,9.57,9.74,9.91)
            SD = c(4.03,3.99,4.11,4.37,4.74,5.21,5.74,6.32,6.94,7.59,8.25,8.94,9.64,10.35,11.07,11.8,12.54,13.28,14.03,14.79,15.55)
            start = 1000
            step = 360
            value <- function(s, duration){
            index = s/5
            for (i in 1:duration){
            start = start*((avg[index]/100)+1)
            start = start + step
            }
            start
            }
            value(65, 10)

            # I used an input of 65% stock and a duration of 10 years here, and my result is 76676.9 after 10 years

1.2)

        stockwithsd = seq(0, 100, 5)
        avg = c(5.09,5.4,5.7,6,6.29,6.57,6.84,7.11,7.37,7.62,7.87,8.11,8.34,8.56,8.78,8.99,9.19,9.38,9.57,9.74,9.91)
        SD = c(4.03,3.99,4.11,4.37,4.74,5.21,5.74,6.32,6.94,7.59,8.25,8.94,9.64,10.35,11.07,11.8,12.54,13.28,14.03,14.79,15.55)
        start = 1000
        step = 360
        value <- function(s, duration){
        index = s/5
        for (i in 1:duration){
        start = start*((rnorm(n=1, m = avg[index], sd = SD[index])/100)+1)
        start = start + step
        }
        start
        }
        value(65, 10)

        # We use the same function as previously, but modify the avg return for each year using a standard deviation in-built function (rnorm)

3 and 4)  

<!-- -->

```{r}
library(ggpubr)
library(ggplot2)
library(tidyverse)
    library(lubridate)
        stockwithsd = seq(0, 100, 5)
        avg = c(5.09,5.4,5.7,6,6.29,6.57,6.84,7.11,7.37,7.62,7.87,8.11,8.34,8.56,8.78,8.99,9.19,9.38,9.57,9.74,9.91)
        SD = c(4.03,3.99,4.11,4.37,4.74,5.21,5.74,6.32,6.94,7.59,8.25,8.94,9.64,10.35,11.07,11.8,12.54,13.28,14.03,14.79,15.55)
        step = 360
        value <- function(s, duration){
        end = c()
        end1=0
        end2=0
        end3=0
        end4=0
        end5=0
        end6=0
        end7=0
        end8=0
        end9=0
        end10=0
        plotsimu = ggplot()
        simulations <- data.frame(matrix(ncol = 100, nrow = 11))
        simulations[1,]=1000
        simulations$Year = seq(0,10,1)
        index = s/5
        for (j in 1:100){
          countend=0
        start = 1000
        line = c()
        for (i in 1:duration){
        start = start*((rnorm(n=1, m = avg[index], sd = SD[index])/100)+1)
        start = start + step
        line = append(line, start)
        if (start >= 5000 & countend==0){
          countend = countend +1
        end = append(end, i)
        if(i == 1){
          end1 = end1+1
        }
        if(i == 2){
          end2 = end2+1
        }
        if(i == 3){
          end3 = end3+1
        }
        if(i == 4){
          end4 = end4+1
        }
        if(i == 5){
          end5 = end5+1
        }
        if(i == 6){
          end6 = end6+1
        }
        if(i == 7){
          end7 = end7+1
        }
        if(i == 8){
          end8 = end8+1
        }
        if(i == 9){
          end9 = end9+1
        }
        if(i == 10){
          end10 = end10+1
        }
        }
        }
        simulations[2:11,j]=line
        }
        output = c(start, end)
        View(simulations)
    plotsimu=ggplot()+geom_line(data = simulations, mapping = aes(x=Year,y=X1))
 
    
    
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X2))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X3))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X4))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X5))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X6))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X7))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X8))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X9))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X10))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X11))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X12))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X13))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X14))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X15))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X16))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X17))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X18))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X19))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X20))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X21))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X22))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X23))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X24))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X25))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X26))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X27))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X28))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X29))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X30))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X31))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X32))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X33))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X34))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X35))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X36))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X37))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X38))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X39))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X40))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X41))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X42))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X43))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X44))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X45))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X46))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X47))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X48))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X49))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X50))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X51))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X52))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X53))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X54))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X55))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X56))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X57))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X58))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X59))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X60))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X61))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X62))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X63))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X64))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X65))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X66))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X67))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X68))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X69))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X70))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X71))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X72))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X73))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X74))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X75))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X76))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X77))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X78))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X79))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X80))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X81))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X82))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X83))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X84))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X85))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X86))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X87))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X88))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X89))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X90))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X91))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X92))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X93))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X94))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X95))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X96))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X97))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X98))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X99))
     plotsimu = plotsimu +geom_line(data = simulations, mapping = aes(x=Year,y=X100))
     plotsimu = plotsimu + theme_minimal()+labs(x="Year",y="Money",
               title="Evolution of amount per year over 100 simulations")
avgtime=Reduce("+", end)/100
plotsimu = plotsimu + geom_vline(xintercept=avgtime, linetype='dashed',col='blue')+geom_hline(yintercept = 5000,linetype='dashed',col='blue')+geom_text(aes(x=avgtime, label="avg time", y=0), colour="blue")
        proba <- data.frame(matrix(ncol = 11,nrow = 1))
        proba[1]=0
        proba[2]=end1
        proba[3]=end1+end2
        proba[4]=end1+end2+end3
        proba[5]=end1+end2+end3+end4
        proba[6]=end1+end2+end3+end4+end5
        proba[7]=end1+end2+end3+end4+end5+end6
        proba[8]=end1+end2+end3+end4+end5+end6+end7
        proba[9]=end1+end2+end3+end4+end5+end6+end7+end8
        proba[10]=end1+end2+end3+end4+end5+end6+end7+end8+end9
        proba[11]=end1+end2+end3+end4+end5+end6+end7+end8+end9+end10
        proba=proba/100
        proba=rbind(proba, seq(0,10,1))
        proba=t(proba)
        proba<-as.data.frame(proba)
        plotproba=ggplot(proba, aes(x = V2, y=V1))+ geom_col()+labs(x="Year",y="probability",
               title="Probabiliy of reaching target per year") + theme_minimal()
        
        ggarrange(plotsimu,plotproba)
        }
      value(30, 10)
```


